\documentclass[11pt,a4paper]{article}
\usepackage{palatino,epsfig}
\usepackage[latin1]{inputenc}
\usepackage[T1]{fontenc}
\usepackage{latexsym}
\usepackage{pstcol}

%\usepackage{fullpage}
\topmargin  -0.5in  % distance to headers
%\headheight 0.2in   % height of header box
\headsep    0.3in   % distance to top line
\textheight 9.0in   % height of text
\footskip   0.3in   % distance from bottom line
%\footheight 0.2in   % height of footer box

% Horizontal alignment

\oddsidemargin  0.in \evensidemargin 0.in \textwidth  6.5in

\title{Implementation of the Machine Description System}
\author{Beno\^{\i}t Dupont de Dinechin}
\date{%
$Revision: 1.5 $
}

\begin{document}
\maketitle

\begin{abstract}

We describe the implementation choices made during the prototyping of the
Machine Description System.

\end{abstract}

\section{Configuration Management}

Typical steps for extraction and configuration of the MDS are (assuming
\texttt{bash} shell):

\begin{verbatim}
  export CVSROOT=/home/tmp/cvsroot
  export PATH=/home/tmp/local/bin:$PATH
  cvs co MDS
  mkdir st230
  cd st230
  ../MDS/configure --target=st230
  make all
  make doc
  make check
  make clean
\end{verbatim}
 
\section{Processing Overview}

The build process (\texttt{make all}) first goes into \texttt{MDS/FE/CHESS} to
build the Machine Description Database (MDD) XML files from the CHESS
\texttt{.db} files and put them under \texttt{MDS/MDD}. Then it goes into
\texttt{MDS/MDE} and creates the Machine Description Expansion (MDE) XML files
under \texttt{MDS/MDE}.  Last, it goes into the \texttt{MDS/BE} subdirectories
and creates the machine description files suited for the different target tools.

\section{Source Code Organization}

\begin{description}

\item[\texttt{MDS/DOC}] Documentation for the MDS, including the XML Document
Type Definition (DTD) for the MDD and the MDE.

\item[\texttt{MDS/DOC/Mail}] Mail exchanged about the design of the XML MDS.

\item[\texttt{MDS/LIB}] Perl modules used by the Perl scripts of the MDS. This
includes pure-Perl CPAN modules like XML::Parser::Lite, and MDS specific Perl
modules.

\item[\texttt{MDS/FE/CHESS}] CHESS front-end of the MDS.

\item[\texttt{MDS/FE/CHESS/st231}] CHESS \texttt{.db} files for the ST231.

\item[\texttt{MDS/FE/CHESS/BIN}] Perl scripts to convert the CHESS \texttt{.db}
files into the \texttt{MDS/MDD} XML files. There is one Perl script for each
\texttt{MDS/MDD} XML file.

\item[\texttt{MDS/MDE/BIN}] Perl scripts to expand the \texttt{MDS/MDD} XML
files into the \texttt{MDS/MDE} XML files. There is one Perl script for each
\texttt{MDS/MDE} XML file.

\item[\texttt{MDD/BE/DOC/BIN}] Perl scripts to produce the HTML documentation
derived from the MDD files.

\item[\texttt{MDD/BE/GNU/BIN}] Perl scripts to produce the \texttt{.c} and
\texttt{.h} files required to target the GNU tools.

\end{description}

\end{document}

